Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-11-04 article.tex
Response to Reviewer #2

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}

@@

\subsubsection{Statistical Analysis}
All statistical analyses were also performed using MATLAB. The differences between arterial, venous, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons. $p \leq 0.05$ was considered statistically significant.

@@

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:timecourse}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:timecourse}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:timecourse}b. The width of the two vessels remained steady throughout the entirety of the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the percent change in vascular flux and parenchymal tissue perfusion as shown in Fig.~\ref{fig:timecourse}c. The vascular flux in R1 and R2 increased by 270\% and 144\%, respectively, while the tissue perfusion in R3 grew by 141\%. The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had minimal effect on the vessel size. Repeated measurements in the subject (Figs.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

@@

@@

While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}. Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a narrow range of flow rates \cite{Parthasarathy:2008el}. Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the surface vasculature. Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%. The repeatability of the day-to-day measurements shown in Figs.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.

>>>>

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}
\usepackage{booktabs}

@@

\subsubsection{Statistical Analysis}
All statistical analyses were also performed using MATLAB. Paired sample t-tests were used to compare awake and anesthetized measurements across vessel diameter and CBF metrics. The differences between arterial, venous, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons. The significance level ($\alpha$) was set to 0.05 for all statistical tests.

@@

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:timecourse}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:timecourse}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:timecourse}b. The width of the two vessels remained steady throughout the entirety of the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the percent change in vascular flux and parenchymal tissue perfusion as shown in Fig.~\ref{fig:timecourse}c. The vascular flux in R1 and R2 increased by 270\% and 144\%, respectively, while the tissue perfusion in R3 grew by 141\%. The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had minimal effect on the vessel size. Repeated measurements in the subject (Fig.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

@@

The differences between awake and anesthetized measurements across vessel diameter and CBF metrics are summarized in Table \ref{tab:awakeanes}. Paired samples t-tests were performed on data aggregated across all subjects and imaging sessions in each state. Paired measurements from 33 arteries, 29 veins, and 46 parenchyma regions were included in the analysis. There were significant differences between the awake and anesthetized measurements for all tested metrics.

% Table 1 - Aggregated Awake vs. Anesthetized Summary
\begin{table}[]
    \caption {
        Paired samples t-tests comparing differences between awake and anesthetized measurements across vessel diameter and blood flow metrics ($\alpha = 0.05$).
    }
    \label{tab:awakeanes}
    \centering
    \begin{tabular}{llccc} 
        \addlinespace
        \toprule
        \textbf{Metric} & \textbf{Region}  & \textbf{$\boldsymbol{t}$} & \textbf{$\boldsymbol{df}$} & \textbf{$\boldsymbol{p}$} \\
        \midrule
        Vessel Dia.     & Artery ($\mu$m)  & -6.15                     & 32                         & $\num{7.1e-7}$            \\
                        & Vein ($\mu$m)    & -3.67                     & 28                         & 0.001                     \\
        \midrule
        Blood Flow      & Artery (Flux)    & -10.75                    & 32                         & $\num{3.7e-12}$           \\
                        & Vein (Flux)      & -4.96                     & 28                         & $\num{3.1e-5}$            \\
                        & Parenchyma (ICT) & -18.44                    & 45                         & $\num{1.3e-22}$           \\
        \bottomrule
    \end{tabular}
\end{table}

@@

While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}. Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a narrow range of flow rates \cite{Parthasarathy:2008el}. Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the surface vasculature. Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%. The repeatability of the day-to-day measurements shown in Fig.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
